Algorithm explanation

### 2013-04-21 article/algo.tex
Explanation on constraint duplication

\begin{align*}
C_v = & \bigcup_{(u,v) \in E} C_u
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \nexists u. u <^+ v \\
\left\lbrace
 \mathbf{a}_v = \sum_{u <^+ v} \mathbf{a}_u,
 b_v \geq \sum_{u <^+ v} b_u
\right\rbrace
& \mbox{otherwise}
\end{cases}
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \varphi(v) = P(\mathbf{x}) \\
\left\lbrace
 \lambda_v \geq 0, \mathbf{a}_v = \lambda_v \mathbf{a}_0,
 b_v = \lambda_v b_0
\right\rbrace
& \mbox{if } \varphi(v) = \mathbf{a}_0 \mathbf{x} \leq b_0
\end{cases}
\end{align*}

@@

If $G$ has a vertex which has multiple successors, the second case is
possible. We now consider to give a solution to the such case.

Let $\hat u$ be a vertex with multiple successors denoted by
$succ(u)$. We now duplicate to relax the linear constraints.

The $\textsc{Copy}$ duplicates a given linear constraint by renaming
all variables to fresh ones. $\mathbf{a'}$ and $b'$ are renamed
variables from $\mathbf{a}$ and $b$ respectively.

Obtaining $G'$ after the transformation above, if $C_{v_\top}$ becomes
satisfiable, a solution $\rho$ to $G$ is given by using solution
$\rho'$ to $G'$:

\begin{align*}
 \rho = \rho' \cup \left\lbrace P = \bigwedge_i \rho'[P_i] \middle|
 \varphi(\hat u) = P(\mathbf{x}) \right\rbrace
\end{align*}

$\forall u \in V. \path{u}{v} \wedge \varphi(u) = P(\mathbf{x}).
$

Note that predicate variables on  than $\hat u$ may
also have duplicated assignments, which should be combined in the
same manner as $P$ above.

If $C_{v_\bot}$ stays unsatisfiable in $G'$, we can repeat the
transformation until no vertices have multiple successors.

>>>>

\begin{align*}
C_v = & \bigcup_{u <^+ v} C_u
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \nexists u. u <^+ v \\
\left\lbrace
 \mathbf{a}_v = \sum_{u <^+ v} \mathbf{a}_u,
 b_v \geq \sum_{u <^+ v} b_u
\right\rbrace
& \mbox{otherwise}
\end{cases}
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \varphi(v) = P(\mathbf{x}) \\
\left\lbrace
 \lambda_v \geq 0, \mathbf{a}_v = \lambda_v \mathbf{a}_0,
 b_v = \lambda_v b_0
\right\rbrace
& \mbox{if } \varphi(v) = \mathbf{a}_0 \mathbf{x} \leq b_0
\end{cases}
\end{align*}

@@

If $G$ has a vertex which has multiple successors, the second case is
possible. We now try to give a solution by relaxing the constraint
$C_{v_\bot}$.

We slightly modify the definition $C_v$. Let $\hat V$ a subset of
vertices with multiple successors.

\begin{align*}
C_v = & \bigcup_{\substack{u <^+ v \\ u \not\in \hat V}} C_u \cup
\bigcup_{\substack{u <^+ v \\ u \in \hat V}} \textsc{Copy}_v (C_u)
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \nexists u. u <^+ v \\
\left\lbrace
 \mathbf{a}_{v,\emptyset} =
  \sum_{\substack{u <^+ v \\ u \not\in \hat V}} \mathbf{a}_{u,U} +
  \sum_{\substack{u <^+ v \\ u \in \hat V}} \mathbf{a}_{u,U \cup \left\lbrace v \right\rbrace},
 b_{v,\emptyset} \geq
  \sum_{\substack{u <^+ v \\ u \not\in \hat V}} b_{u,U} +
  \sum_{\substack{u <^+ v \\ u \in \hat V}} b_{u,U \cup \left\lbrace v \right\rbrace}
\right\rbrace
& \mbox{otherwise}
\end{cases}
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \varphi(v) = P(\mathbf{x}) \\
\left\lbrace
 \lambda_v \geq 0, \mathbf{a}_{v,\emptyset} = \lambda_v \mathbf{a}_0,
 b_{v,\emptyset} = \lambda_v b_0
\right\rbrace
& \mbox{if } \varphi(v) = \mathbf{a}_0 \mathbf{x} \leq b_0
\end{cases}
\end{align*}

The procedure $\textsc{Copy}_v$ renames all free variables to avoid
name collision. Its definition is given as follows.

\[\textsc{Copy}_{\hat v}(\mathbf{a}_{u,V}) = \mathbf{a}_{u,(V \cup
  \left\lbrace \hat v \right\rbrace)} \]

All variables are then distinguished by the label of copy origin
nodes. This intuitively means that constraints generated for nodes in
$\hat V$ are duplicated at their successors. Note that the variables
without the label should be interpreted as that it has $\emptyset$ for
origin nodes.

When $C_{v_\bot}$ becomes satisfiable by specifing an appropriate
$\hat V$, a solution $\rho$ to $G$ is given as follows.

\begin{align*}
 \rho = \left\lbrace
  \left( P, \bigwedge_S \sigma(\mathbf{a}_{v,S} \mathbf{x} \leq b_{v,S}) \right) \middle|
  \forall v \in V. \varphi(v) = P(\mathbf{x})
 \right\rbrace
\end{align*}

If $C_{v_\bot}$ stays unsatisfiable, we can add a vertex with multiple
successors to $\hat V$ until all such nodes are in $\hat V$.
